AFQ-Insight

### 2019-12-01 reports/manuscript/sections/results.tex
Small things.

Using data from a previous study of the corticospinal tract profile and
ALS\cite{sarica2017corticospinal}, we tested the performance of SGL in a
classification setting. The previous study predicted ALS status with a mean
accuracy of 80\% using a random forest algorithm based on a priori selection of
features within the corticospinal tract. SGL delivers competitive predictive
performance (mean 93\% $\pm$ 2\% accuracy, 0.978 $\pm$ 0.006 ROC AUC) without
the need for a priori feature engineering. The results of the classification
prediction are shown in Fig~\ref{fig:class-results}, with ``ground-truth'' ALS
status separated into columns, and predicted ALS status encoded by color. In
addition to this classification performance, SGL also identifies the white
matter tracts most important for ALS classification. The relative importance of
white matter features is captured in the $\beta$ coefficients from
Eq~\eqref{eq:sgl}. Fig~\ref{fig:class-beta} depicts these coefficients across
the brain, laid out on a skeleton of the major tracts. We find that SGL selects
FA metrics in the corticospinal tract and particualrly in the right
corticospinal tract as most important to ALS classification, confirming previous
findings\cite{van2011upper, toosy2003diffusion, sarica2014tractography,
sage2007quantitative, sage2009quantitative, karlsborg2004corticospinal,
ellis1999diffusion, cosottini2005diffusion, ciccarelli2009investigation,
abe2010voxel} and identifying exactly the portions of the brain that were
selected \emph{a priori} in the previous study from which we collected our
data\cite{sarica2017corticospinal}.

@@

    \caption{{\bf SGL accurately predicts ALS.}
        Left: Classification probabilities for each subject's ALS diagnosis.
        Controls are on the left while patients are on the right. Predicted
        controls are in blue and predicted patients are in red. Thus, false
        positive are represented as red dots on the left, while false negatives
        are represented as blue dots on the right. The SGL algorithm achieves
        93\% $\pm$ 2\% accuracy,with 0.978 $\pm$ 0.006 ROC AUC. Right: SGL
        coefficients are presented on a skeleton of the major tracts. The brain
        is oriented with the right hemisphere to our left and anterior out of
        the page. As expected large negative coefficients are in the FA of the
        corticospinal tract (and particularly right CST, here to the left)}
    \label{fig:class-results}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.95\textwidth]{classification_tract_profiles.pdf}
    \caption{{\bf Model coefficients mirror FA differences}. The places along the
       length of the corticospinal tract where $\hat{\beta}$ coefficients for FA
       (dashed line, right axis) have large negative values correspond to the
       locations of substantial differences between the ALS (green) and control
       (orange) FA (shaded area indicates standard error of the mean).}
    \label{fig:class-profiles}
\end{figure}

\begin{figure}[!h]
    \centering
        \includegraphics[width=0.95\textwidth]{classification_subjects_profiles.pdf}
    \caption{{\bf Model mis-classifications correspond to features identified by the model}.
       They make sense}
    \label{fig:class-errors}
\end{figure}

>>>>

Using data from a previous study of the corticospinal tract (CST) profile and
ALS\cite{sarica2017corticospinal}, we tested the performance of SGL in a
classification setting. The previous study predicted ALS status with a mean
accuracy of 80\% using a random forest algorithm based on a priori selection of
features within the corticospinal tract. SGL delivers competitive predictive
performance (mean 93\% $\pm$ 2\% accuracy, 0.978 $\pm$ 0.006 ROC AUC) without
the need for a priori feature engineering. The results of the classification
prediction are shown in Fig~\ref{fig:class-results}, with ``ground-truth'' ALS
status separated into columns, and predicted ALS status encoded by color. In
addition to this classification performance, SGL also identifies the white
matter tracts most important for ALS classification. The relative importance of
white matter features is captured in the $\beta$ coefficients from
Eq~\eqref{eq:sgl}. Fig~\ref{fig:class-beta} depicts these coefficients across
the brain, laid out on a skeleton of the major tracts. We find that SGL selects
FA metrics in the corticospinal tract and particualrly in the right
corticospinal tract as most important to ALS classification, confirming previous
findings\cite{van2011upper, toosy2003diffusion, sarica2014tractography,
sage2007quantitative, sage2009quantitative, karlsborg2004corticospinal,
ellis1999diffusion, cosottini2005diffusion, ciccarelli2009investigation,
abe2010voxel} and identifying exactly the portions of the brain that were
selected \emph{a priori} in the previous study from which we collected our
data\cite{sarica2017corticospinal}.

@@

    \caption{{\bf SGL accurately predicts ALS.}
        Left: Classification probabilities for each subject's ALS diagnosis.
        Controls are on the left while patients are on the right. Predicted
        controls are in blue and predicted patients are in red. Thus, false
        positive are represented as red dots on the left, while false negatives
        are represented as blue dots on the right. The SGL algorithm achieves
        93\% $\pm$ 2\% accuracy,with 0.978 $\pm$ 0.006 ROC AUC. Right: SGL
        coefficients are presented on a skeleton of the major tracts. The brain
        is oriented with the right hemisphere to our left and anterior out of
        the page. As expected large negative coefficients are in the FA of the
        CST (and particularly in the right hemisphere, here to the left)}
    \label{fig:class-results}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.95\textwidth]{classification_tract_profiles.pdf}
    \caption{{\bf Model coefficients mirror FA differences}. The places along the
       length of the CST  where $\hat{\beta}$ coefficients for FA
       (dashed line, right axis) have large negative values correspond to the
       locations of substantial differences between the ALS (green) and control
       (orange) FA (shaded area indicates standard error of the mean).}
    \label{fig:class-profiles}
\end{figure}

\begin{figure}[!h]
    \centering
        \includegraphics[width=0.95\textwidth]{classification_subjects_profiles.pdf}
    \caption{{\bf Model mis-classifications correspond to features identified by
       the model}. The FA in CST of individuals that are mis-classified by the
       model is compared the group FA (with shaded are indicating standard error
       of the mean). False negative classifications (individuals that have ALS,
       but are classified as patients have) correspond to high FA either in the
       more inferior part of the CST}
    \label{fig:class-errors}
\end{figure}
